MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-24 paper.Rmd
Better targets URL.

| Package | Function |
|:--------|:---------|
| [IEATools](https://matthewheun.github.io/IEATools/) | Converts IEA data to PSUT format |
| [Recca](https://matthewheun.github.io/Recca/)       | Performs `R` energy conversion chain analysis |
| [PFUDatabase](https://energyeconomydecoupling.github.io/PFUDatabase/) | The [targets](https://books.ropensci.org/targets/) pipeline to create a data frame of PSUT matrices |
| [PFUAggDatabase](https://energyeconomydecoupling.github.io/PFUAggDatabase/) | The [targets](https://books.ropensci.org/targets/) pipeline to aggregate PSUT matrices created by the [PFUDatabase](https://energyeconomydecoupling.github.io/PFUDatabase/) pipeline |

>>>>

| Package | Function |
|:--------|:---------|
| [IEATools](https://matthewheun.github.io/IEATools/) | Converts IEA data to PSUT format |
| [Recca](https://matthewheun.github.io/Recca/)       | Performs `R` energy conversion chain analysis |
| [PFUDatabase](https://energyeconomydecoupling.github.io/PFUDatabase/) | A [targets](https://docs.ropensci.org/targets/) pipeline to create a data frame of PSUT matrices |
| [PFUAggDatabase](https://energyeconomydecoupling.github.io/PFUAggDatabase/) | A [targets](https://docs.ropensci.org/targets/) pipeline to aggregate PSUT matrices |
